Implications of animal movement rate variation in spatial patterns of seed dispersal

### 2021-11-08 Ch1_movement_rates/Ch1_Figures.Rmd
Saving results figures.

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  NULL -> logfit_plot

@@

fam_moverate %>%
  ggplot(., aes(x = movrate, y = -0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  glines +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", y = "Density",
       title = "Distribution for social group movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6)) -> social_group_curves

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Model scenario",
       title = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  NULL-> movrates_used

@@

```{r fig.height=12, fig.width=6}
plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1))

@@

# Figure x - seed dispersal kernel parameters
Here we are using the distance of each seed

@@

## Variation 2 - violin plot with all 1000 of the parameter fits

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

## Variation 3 - boxplot with all the fits, 1000

```{r}
joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.shape)) +
  geom_boxplot() +
  # geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  #geom_jitter(position = position_jitter(0.1)) +
  geom_hline(aes(yintercept = 1), lty = "dashed") +
  labs(title = "Shape") +
  #scale_y_continuous(limits = c(0, 2)) +
  theme_bw() -> weib_shape

joint_weib %>%
  group_by(model) %>%
  sample_n(., 1000) %>%
  ggplot(., aes(x = model, y = est.scale)) +
  geom_boxplot() +
  #geom_violin() +
  # scale_color_manual(values = c("black", mycols)) +
  # geom_boxplot(width = 0.01) +
  # geom_point(color = "grey", alpha = 0.5) +
  # stat_summary(fun.data=mean_sdl, mult=1,
  #              geom="pointrange", color="black") +
  #geom_jitter(position = position_jitter(0.1)) +
  labs(title = "Scale") +
  theme_bw() -> weib_scale

>>>>

indiv_moverate %>%
  ggplot(., aes(x = movrate, y = 0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  # geom_point(data = fam_moverate, aes(x = movrate, y = 0.004),size = 3, alpha = 0.8, color = my.cols1[4]) +
  stat_function(fun = dlnorm, args = list(meanlog = logfit$estimate[1], sdlog = logfit$estimate[2]),
                color = "black", alpha = 0.8, size = 1) +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)",
       y = "Density",
       subtitle = "Lognormal fit to individual movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank()) +
  NULL -> logfit_plot

@@

fam_moverate %>%
  ggplot(., aes(x = movrate, y = -0.002, color = fam_g)) +
  geom_point(size = 3, alpha = 0.8) +
  glines +
  scale_color_manual(values = cols.fig2) +
  labs(x = "Movement Rate (meters/minute)", 
       y = "Density",
       subtitle = "Distribution for social group movement rates") +
  #geom_vline(xintercept = vlines, color = my.cols1[4], size = 1, lty = 2) +
  scale_x_continuous(limits = c(0, 70)) +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = c(0.8, 0.6),
        axis.title.x = element_blank()) -> social_group_curves

movratedf %>% 
  ggplot(., aes(x = movrate, y = factor(scenario, levels = c("pp", "np", "cp")), color = as.character(group))) +
  geom_jitter(size = 3, alpha = 0.8, height = 0.1) +
  scale_color_manual(values = cols.fig2) +
  scale_x_continuous(limits = c(0, 70)) +
  labs(x = "Movement Rate (meters/minute)", y = "Scenario",
       subtitle = "Sampled movement rates for each simulated scenario") +
  #scale_x_discrete(labels = c(0, vlines[1], 20, vlines[2], 40, vlines[3], 60)) +
  guides(color = guide_legend(title = "Social Group",
                              ncol = 2)) +
  theme_bw() +
  theme(legend.position = "none") +
  NULL-> movrates_used

@@

```{r fig.height=7, fig.width=5}
plot_grid(logfit_plot, social_group_curves, movrates_used, nrow = 3, rel_heights = c(2,2,1), labels = "AUTO")

@@

# Figure 5 - seed dispersal kernel parameters
Here we are using the distance of each seed

@@
